---
title: "Ecocide Austria"
format:
  html:
    self-contained: false
    theme: cosmo
    toc: false
    toc-depth: 3
    code-fold: true
    code-summary: "Show Code"
    page-layout: full
    grid:
      margin-width: 100px
      body-width: 1100px
editor: source
execute:
  echo: true
  warning: false
  message: false
  freeze: auto
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, waring = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(glue)
library(sf)
library(davR)
library(jsonlite)
library(mapview)
m <- mapview
library(leaflet)
library(DT)
library(crosstalk)
library(htmlwidgets)


# ++++++++++++++++++++++++++++++
# read in data ----
# ++++++++++++++++++++++++++++++
geo_omv_dafni_8857 <- read_sf(
    "~/Library/Mobile Documents/com~apple~CloudDocs/geodata/projects_data_raw/2025-10-ecocide/data_dafni/Austria-all-blocks.gpkg"
)

geo_pa_8857 <- read_sf(
    "~/Library/Mobile Documents/com~apple~CloudDocs/geodata/projects_data_raw/2025-10-ecocide/output/wdpa/austria/wdpa_austria_polygons.gpkg"
) %>%
    st_transform(8857)


# ++++++++++++++++++++++++++++++
# intersections ----
# ++++++++++++++++++++++++++++++
geo_omv_dafni_8857 <- geo_omv_dafni_8857 %>%
    rename_with(~ paste0("ms_", .), .cols = -attr(., "sf_column"))

geo_pa_8857 <- geo_pa_8857 %>%
    rename_with(~ paste0("pa_", .), .cols = -attr(., "sf_column"))

geo_int_blocks_pa <- st_intersection(
    geo_pa_8857,
    geo_omv_dafni_8857
)

geo_int_blocks_pa %>%
    select(
        ms_descriptio,
        ms_name,
        ms_adm_co_gro,
        ms_adm_co_nam,
        ms_admin_area,
        ms_attributio,
        ms_lc_status,
        ms_lc_type,
        ms_mps_create,
        ms_mps_dataso,
        pa_NAME,
        pa_ORIG_NAME,
        pa_DESIG,
        pa_DESIG_ENG,
        pa_DESIG_TYPE,
        pa_IUCN_CAT,
        pa_INT_CRIT,
        pa_GOV_TYPE
    ) -> geo_int_pa_ms_at


# write out intersections
path_out_intersections <- sys_make_path(here(
    "data_output/intersections_mapstand_pa_austria/intersections_mapstand_pa_austria.fgb"
))
unlink(path_out_intersections)
write_sf(geo_int_pa_ms_at %>% st_transform(4326), path_out_intersections)

# ++++++++++++++++++++++++++++++
# get only OMV ----
# ++++++++++++++++++++++++++++++
geo_int_pa_ms_at_omv <- geo_int_pa_ms_at %>%
    filter(str_detect(ms_adm_co_gro, "OMV"))
```

```{r}
# Dramatically simplify geometries for the overview map to reduce file size
tolerance <- 500 # meters
geo_omv_dafni_simple <- st_simplify(geo_omv_dafni_8857, dTolerance = tolerance)
geo_pa_simple <- st_simplify(geo_pa_8857, dTolerance = tolerance)
geo_int_omv_simple <- st_simplify(geo_int_pa_ms_at_omv, dTolerance = tolerance)

# Reproject data to WGS 84 (EPSG:4326) for leaflet
geo_omv_dafni_4326 <- st_transform(geo_omv_dafni_simple, crs = 4326)
geo_pa_4326 <- st_transform(geo_pa_simple, crs = 4326)
geo_int_omv_4326 <- st_transform(geo_int_omv_simple, crs = 4326)

# Replace mapview with a more efficient leaflet map
leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron, group = "Basemap") %>%
    addPolygons(
        data = geo_pa_4326,
        fillColor = "#7d7d7d",
        fillOpacity = 0.4,
        stroke = FALSE,
        group = "Protected Areas"
    ) %>%
    addPolygons(
        data = geo_omv_dafni_4326,
        fillColor = "#2b2b2b",
        fillOpacity = 0.4,
        stroke = FALSE,
        group = "Mapstand Data"
    ) %>%
    addPolygons(
        data = geo_int_omv_4326,
        fillColor = "tomato",
        fillOpacity = 0.7,
        color = "red",
        weight = 1,
        dashArray = "10",
        group = "Intersection"
    ) %>%
    addLayersControl(
        overlayGroups = c("Protected Areas", "Mapstand Data", "Intersection"),
        options = layersControlOptions(collapsed = FALSE)
    )
```

# Which types of interscetion?

```{r}
options(scipen = 999)
geo_intersections_areas <- geo_int_pa_ms_at_omv %>%
    mutate(
        area_intersection_sqm = st_area(.),
        area_intersection_sqkm = st_area(.) / 1e6,
        area_intersection_ha = st_area(.) / 10000,
    )
total_intersection_sqkm <- sum(geo_intersections_areas$area_intersection_sqkm)
```

<div style="font-size: 1.2em; font-weight: bold; color: tomato; margin-bottom: 1em;">
Total intersection area is `r round(units::drop_units(total_intersection_sqkm), 2)` sqkm.
</div>

### Intersections by Protected Area Type


```{r}
# First, create the summarized data with a clean area column
sf_intersections_by_type <- geo_intersections_areas %>%
    group_by(pa_DESIG_ENG, pa_DESIG) %>%
    summarise(
        total_area_sqkm = sum(area_intersection_sqkm, na.rm = TRUE),
        .groups = "drop"
    ) %>%
    mutate(total_area_sqkm = units::drop_units(total_area_sqkm))

# Simplify, reproject, and add a zoom-to link for the table
sf_intersections_with_zoom <- sf_intersections_by_type %>%
    st_simplify(dTolerance = 10) %>%
    st_transform(crs = 4326) %>%
    mutate(
        key = row_number(), # Add a unique key for each row
        centroid = st_point_on_surface(.), # Use '.' to refer to the sf object
        lng = st_coordinates(centroid)[, 1],
        lat = st_coordinates(centroid)[, 2],
        zoom = paste0(
            '<a class="go-map" href="#" data-key="',
            key,
            '">',
            '<i class="bi bi-geo-alt-fill"></i></a>'
        )
    ) %>%
    select(zoom, everything(), -centroid, -lng, -lat)

# Wrap the data in a SharedData object for crosstalk, using the new key
shared_intersections <- SharedData$new(sf_intersections_with_zoom, key = ~key)
```


::: {.column-page}
::: {layout-ncol=2}

```{r}
datatable(
    shared_intersections,
    escape = FALSE, # Important: Renders the zoom icon HTML
    extensions = "Buttons",
    options = list(
        dom = "Bt",
        buttons = c("csv", "excel"),
        scrollY = "400px",
        paging = FALSE,
        columnDefs = list(
            list(visible = FALSE, targets = c("geom", "key"))
        )
    ),
    rownames = FALSE
) %>%
    formatRound("total_area_sqkm", digits = 2) %>%
    formatStyle(
        "total_area_sqkm",
        color = "tomato",
        fontWeight = "bold"
    )
```


```{r}
# The Map, with custom JavaScript to handle persistent highlighting on click
leaflet(shared_intersections) %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    addPolygons(
        layerId = ~key, # Assign the unique key as the layerId
        weight = 2,
        fillOpacity = 0.7,
        color = "tomato",
        label = ~ glue::glue("{pa_DESIG_ENG}: {round(total_area_sqkm, 2)} sqkm")
    ) %>%
    onRender(
        sprintf(
            "
    function(el, x) {
      var map = this;
      var group = '%s';

      // Define the three style states
      var defaultStyle = { 'weight': 2, 'fillOpacity': 0.7, 'color': 'tomato', 'fillColor': 'tomato' };
      var highlightStyle = { 'weight': 4, 'color': 'black', 'fillColor': 'yellow', 'fillOpacity': 0.8 };
      var ghostStyle = { 'fillOpacity': 0.1, 'stroke': false };

      function findLayerByKey(key) {
        var foundLayer = null;
        map.eachLayer(function(layer) {
          if (layer.options && layer.options.layerId == key) {
            foundLayer = layer;
          }
        });
        return foundLayer;
      }

      var ct_selection = new crosstalk.SelectionHandle(group);

      // Listen for changes on the selection handle
      ct_selection.on('change', function(e) {
        var selectedKey = (e.value && e.value.length > 0) ? e.value[0] : null;

        map.eachLayer(function(layer) {
          // Act on our data layers (which have a layerId)
          if (layer.options && layer.options.layerId) {
            if (selectedKey) { // A selection is active
              if (layer.options.layerId == selectedKey) {
                layer.bringToFront();
                layer.setStyle(highlightStyle);
              } else {
                layer.setStyle(ghostStyle);
              }
            } else { // No selection, restore all to default
              layer.setStyle(defaultStyle);
            }
          }
        });
      });

      // Add click listener to each polygon layer for two-way binding
      map.eachLayer(function(layer) {
        if (layer.options && layer.options.layerId) {
          layer.on('click', function(e) {
            var key = e.target.options.layerId;
            var current_selection = ct_selection.value;

            if (current_selection && current_selection[0] === key) {
              ct_selection.clear(); // If already selected, clear the selection
            } else {
              ct_selection.set([key]); // Otherwise, set the new selection
            }
          });
        }
      });

      // Keep the existing zoom-to-feature logic
      $(document).on('click', '.go-map', function(e) {
        e.preventDefault();
        var $el = $(this);
        var key = $el.data('key'); // Get the key from the link
        var layer = findLayerByKey(key);
        if (layer) {
          map.fitBounds(layer.getBounds());
        }
      });
    }
    ",
            group = shared_intersections$groupName()
        )
    )
```

:::
:::

## Was OMV schreibt:

<style>
mark {
  margin: 0 -0.4em;
  padding: 0.1em 0.4em;
  border-radius: 0.8em 0.3em;
  background: transparent;
  background-image: linear-gradient(
    to right,
    rgba(255, 225, 0, 0.1),
    rgba(255, 225, 0, 0.7) 4%,
    rgba(255, 225, 0, 0.3)
  );
  -webkit-box-decoration-break: clone;
  box-decoration-break: clone;
}
</style>

::: {.callout-note collapse="true"}
## E4 Biodiversity and Ecosystems

[E4-IRO-1.17a] For the identification of impacts, risks, and opportunities, during the materiality assessment, OMV environmental experts applied a top-down qualitative approach to screen OMV’s business activities for actual and potential biodiversity and ecosystem aspects. The value chain was also included in the analysis. In parallel to our materiality assessment, we started to map OMV sites against biodiversity-sensitive areas and to conduct an internal formal assessment for biodiversity risks, in accordance with Environmental Management System policies and the <mark>LEAP (Locate, Evaluate, Assess, Prepare) approach.</mark>

[E4-IRO-1.17a, 17b] The materiality assessment results will be consolidated with a more specific approach in the coming years, which will continue to follow the guidance and phases of LEAP as recommended by the TNFD. In 2023, OMV started to perform a <mark>Group-wide TNFD LEAP assessment</mark> to identify and assess nature-related impacts and risks. In the **Locate** step, all OMV sites were subjected to geospatial analysis to prioritize sites based on ecosystem integrity and biodiversity importance. Various biodiversity data layers provided by integrated biodiversity assessment tools such as layers on protected areas, key biodiversity areas, and IUCN red listed species, as well as freely available layers such as Esri land cover, mean species abundance and water stress were applied. The results of the Locate phase were also used to select six pilot sites across all divisions.

The **Evaluate** step is based on the <mark>direct drivers of biodiversity loss</mark>, which include climate change, land use changes, freshwater use changes, and sea use changes, direct exploitation, invasive alien species, pollution of air, water, and soil, and other factors such as disturbances. Additionally, it considers the impacts on the state of species, as well as impacts on the extent and condition of ecosystems, including issues like land degradation, desertification, and soil sealing. During this stage, a <mark>corporate impact and dependency register</mark> was established by aligning OMV’s activities with data from the ENCORE tool and TNFD sector guidance. The corporate register is used as a starting point for the site-level assessments for the six pilot sites, where the impact drivers are correlated with nature impacts, that is impacts on species, habitats, and ecosystems. To rate the site-level impacts, the magnitude of the effect of nature impacts and receptor sensitivity need to be scored. Dependencies are evaluated in a similar way. The results of the Evaluate phase were used as an input for the **Assess** step, where risks and opportunities are analyzed. To assess biodiversity risks, OMV makes use of a <mark>biodiversity-specific corporate risk register</mark>, which is integrated into OMV’s existing HSSE risk management framework.

In the **Prepare** step, we focused on disclosure, work related to metrics and targets, updating the biodiversity policy, and defining a roadmap for further rollout. As our LEAP assessment is not completed, we cannot disclose a list of material sites yet, nor can we conclude that OMV contributes directly to the impact drivers of land-use changes, freshwater-use changes, and/or sea-use changes. In 2025, we will continue to roll out the LEAP assessment to the remaining priority sites to ultimately yield a list of material sites.

[E4-IRO-1.17c] Following the same scenario used for climate change analysis, the IPCC highlighted how climate change could alter the ecosystems and cause a loss of biodiversity exacerbated by pollution or land use change. By reducing its carbon footprint, OMV intends to minimize the additional stress on nature. In addition, the biodiversity initiatives to which OMV commits are intended to ensure ecosystems protection or restoration that reduces the risk to biodiversity. Nevertheless, OMV commits to further understand the impact of fossil fuel-based business and microplastic on biodiversity. The OMV analysis of biodiversity considers the following dimensions:

*   Climate change-related analysis is well covered in E1
*   Water is a relevant impact driver to understand OMV resilience using the IPCC climate change scenarios and OMV’s water consumptions
*   Potential changes to natural habitats in addition to the factors mentioned above are assumed to have limited implications on OMV activities, considering the nature of the business. This review refers only to the long-term potential implications on OMV’s business, with no analysis of the economic and social resilience in the context of various scenarios used
*   The materiality assessment determined that <mark>there are no transition risks or opportunities associated with biodiversity and ecosystems.</mark> This conclusion was reached after applying assessment criteria based on the biodiversity impacts and dependencies.

[E4-IRO-1.17d] The assessment concluded that <mark>there are no systemic risks associated with biodiversity.</mark> However, it is important to note that systemic risks were thoroughly evaluated and incorporated into the physical climate change analysis. This ensures a comprehensive understanding of potential threats and their broader implications.

[E4-IRO-1.17e-i, 17e-ii] Internal and external stakeholders, including representatives of affected communities, through their proxies, were involved in the materiality assessment through an online survey. The materiality assessment process followed a top-down approach, mainly leveraging the expertise and knowledge of subject matter experts. Consequently, not all relevant criteria were considered, such as specific sites, raw materials production, or sourcing, as our LEAP assessment is still ongoing. [E4-IRO-1.17e-iii] Internal and external stakeholders, including representatives of affected communities, through their proxies, were involved in the materiality assessment through an online survey. The materiality assessment process followed a top-down approach, mainly leveraging the expertise and knowledge of subject matter experts. Consequently, not all relevant criteria were considered, such as specific sites, raw materials production, or sourcing, as our LEAP assessment is still ongoing.

[E4-IRO-1.19, 19a] The assessment by the experts was performed by mapping OMV sites with biodiversity-sensitive areas. We <mark>operate inside or near various types of biodiversity-sensitive areas,</mark> such as nationally protected areas (NPA), Natura 2000 sites, and key biodiversity areas (KBA). Most of these sensitive areas are Natura 2000 sites. According to our assessments, the total site area in or near sensitive areas accounts for a total operational surface as summarized in the table below. It is important to emphasize that the information provided in the table below is <mark>not a statement about negative impacts on sensitive areas.</mark> Rather, it merely indicates the proximity of OMV operations to such areas. As our LEAP assessment is still ongoing, we currently cannot say whether the activities conducted at our sites negatively affect biodiversity-sensitive areas.

**Mapping OMV sites with biodiversity-sensitive areas**
*In ha*

| Division | Country | Area of sites in or near biodiversity-sensitive areas | Types of biodiversity-sensitive areas |
| :--- | :--- | :--- | :--- |
| Chemicals | AT | 75 | NPA, Natura 2000, KBA |
| | BE | 168 | NPA, Natura 2000, KBA |
| | BR | 0 | n.a. |
| | DE | 7 | NPA, Natura 2000 |
| | FI | 79 | NPA, Natura 2000 |
| | IT | 0 | n.a. |
| | NL | 0 | n.a. |
| | SE | 52 | NPA |
| | US | 0 | n.a. |
| Fuels & Feedstock | AT | 318 | NPA, Natura 2000, KBA |
| | DE | 160 | NPA, Natura 2000, KBA |
| | HU | 9 | Natura 2000 |
| | RO | 25 | NPA, Natura 2000, KBA |
| Energy | AT | 25 | NPA, Natura 2000, KBA |
| | NO | 0 | n.a. |
| | NZ | 2 | KBA |
| | RO | 222 | NPA, Natura 2000, KBA |
| | TN | 0 | n.a. |
| | YE | 0 | n.a. |
| **Total** | | **1,141** | **n.a.** |

*Area of sites located in or near biodiversity-sensitive areas in aggregated form (by division and country) is defined as the total area of OMV sites (in ha) that are located within 1 km of biodiversity-sensitive areas. The analysis does not consider the portion of OMV sites that fall within the boundaries of a sensitive area expanded by a 1 km buffer zone. Instead, if any part of the site lies within the 1 km buffer zone, the entire site area is included. In contrast, if any part of the site falls within the 1 km buffer zone, the entire site is considered. For industrial sites in our Fuels & Feedstock and Chemicals divisions, the geospatial analysis was carried out for the entire industrial site as defined by the perimeter fence. This approach cannot be applied to our Energy division sites, as these are made up of a very large number of smaller facilities spread over a large area. Here, a granular analysis based on individual wells and facilities was performed. Since all wells and majority of our facilities are entered as point data (i.e., without area) in our GIS systems, proxy polygons with average areas had to be created and used in the geospatial analysis. For wells, an average proxy area of 900 m2 and for facilities an average proxy area of 5,000 m2 was used in the analysis.*

*Assumptions and limitations on this analysis were mainly related to the use of proxy areas for OMV facilities and wells in the Energy division. In addition, we made the assumption that filling stations, pipelines, and certain types of facilities (e.g., office buildings outside of industrial sites) do not have a impact on biodiversity and ecosystems and therefore were excluded from the analysis. The analysis is performed once per year and as 2024 is the first year that OMV has reported. Primary data (OMV operations) and publicly available data on biodiversity-sensitive areas is used in the assessment.*

[E4-IRO-1.19b] In the assessment, we did not consider biodiversity mitigation measures as outlined in various directives and standards, including Directive 2009/147/EC, Council Directive 92/43/EEC, the Environmental Impact Assessment (EIA) as defined in Directive 2011/92/EU, or equivalent national provisions and international standards such as the IFC Performance Standard 6. The directives will be evaluated and potentially integrated in the future. Impacts and mitigation measures in OMV are defined in accordance with the permits obtained for each of our sites. Mitigation measures are applied for significant impacts identified in agreement with the environmental authorities during the regulatory assessment procedure. Permitting and assessment procedures are applicable in all countries in which we operate. When significant impacts are observed or predicted, the <mark>mitigation hierarchy is followed, and action planning prioritizes the avoidance and minimization of impacts.</mark>
:::